quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-20 paper-quollr.Rmd
Changed the position of the figure

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", out.width="100%", fig.width=15, fig.height=10, eval=knitr::is_latex_output()}

>>>>

```{r model-limb, fig.cap="Compare the published $2-\\text{D}$ layout (Figure \\@ref(fig:limb-rmse) b) and the $2-\\text{D}$ layout selected (Figure \\@ref(fig:limb-rmse) f) by RMSE plot (Figure \\@ref(fig:limb-rmse)) from the tSNE, UMAP, PHATE, TriMAP, and PaCMAP with different (hyper)parameters. The Limb muscle data ($n =  1067$) has seven close different shaped clusters in $10\\text{-}D$.", fig.pos='H', fig.width=15, fig.height=10, eval=knitr::is_latex_output()}
